Notes on Wide Gap

### 2016-05-13 paper/wide_gap_notes.tex
added preliminary N2 figure

-- We locate threshold in the $\reym$ - $k_z$ plane. In the wide-gap case, the growth rate depends much more sensitively on $k_z$ than on $\reym$, while in the thin-gap case the opposite is true. We attribute this to the decreased influence of the boundary layers in the wide-gap geometry. (maybe?)

The complex nature of the MRI means its properties are best parsed in idealized regimes or in simplified geometries. Many studies take

@@

@@

>>>>

%-- We locate threshold in the $\reym$ - $k_z$ plane. In the wide-gap case, the growth rate depends much more sensitively on $k_z$ than on $\reym$, while in the thin-gap case the opposite is true. We attribute this to the decreased influence of the boundary layers in the wide-gap geometry. (maybe?)

%The complex nature of the MRI means its properties are best parsed in idealized regimes or in simplified geometries. Many studies take

@@

-- coefficients of GLE come from inner products, therefore must always be real. Could we ever get a complex GLE?

@@

\begin{figure}[h!]
\centering
\includegraphics[width=\textwidth]{../../weakly_nonlinear_mri/python/widegap/figures/N2_test}
\caption{N2 from unnormalized lower-order components. This is with Rm = 0.845, Q = 0.006. Black = real, teal = imaginary. Why is psi not zero at the boundaries?
\label{fig:firstorder_B}}
\end{figure}
